---
title: "MEDISIS Fishing Effort Map"
author: "Stephanie Hopkins"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}

rm(list = ls())
gc()

knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE, results = "hide")

list.of.packages <- c("data.table","tidyverse","reshape2","cowplot","stars","sf",
                      "ggspatial","ggpattern","ggnewscale", "gtable", "classInt",
                      "ggplotify","gridExtra")

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

library(sf)
library(data.table)
library(stars)
library(cowplot)
library(reshape2)
library(tidyverse)
library(ggspatial) # For North Arrow and Scale Bar
library(ggpattern) # For textured shape file
library(ggnewscale) # For additional color fill palette 
library(gtable)
library(classInt)
library(gridExtra)
library(ggplotify)

# To Replace with your file directory
dir <- "C:/Users/steph/Documents"

MEDISIS <- "/MEDISIS/Part2.Analysing.the.simulation.output/"

path <- paste(dir,MEDISIS,sep="")

```

# Load the european coast line and grid

This will serve as a base map for all other plots. You can actually use the rworldmap and rworldxtra libraries if you do not yet have a shape file.

```{r region.shape}

shapes_subfolder <- "Data/Shape.files/"

GDL_extension <- "Extra/carto/shapefile/Europe_coastline_shapefile/"

GDL <- read_sf(paste(path, shapes_subfolder, GDL_extension, "GDL.shp", sep = ""))
plot(GDL)

# NOTE: Grid extent should be 3, 6, 42.00, 43.55
GDL_crop <- st_crop(GDL, xmin=2.95, xmax=6.05, ymin=41.95, ymax=43.6)
plot(GDL_crop)

grid <- read_sf(paste(path, shapes_subfolder, "Grid/grid.shp", sep = ""))
plot(grid)

p <- ggplot() + 
  geom_sf(data=GDL_crop, color = alpha("grey", 1/2), size = 0.7, fill = 'darkgrey', alpha = .3) + 
  geom_sf(data = grid, color = "grey")

p

rm(GDL)

```

# Load Spatial Closures

```{r closure.shape.files}

FRA <- read_sf(paste(path, shapes_subfolder, "FRA/FRAs_WGS84.shp", sep = ""))
FRA <- FRA[1,]

p + geom_sf(data = FRA, fill = 'yellowgreen', alpha = 0.3)

#---------------------------------------------------------------------------

NewFRA_regulation <- read_sf(paste(path, shapes_subfolder, "NewFRA_regulation/boxPaca_polygon_4326.shp", sep = ""))

p + geom_sf(data = NewFRA_regulation, fill = 'yellowgreen', alpha = 0.3)

#---------------------------------------------------------------------------

zone_90_100_simplified <- read_sf(paste(path, shapes_subfolder, "zone_90_100_simplified/zone_90_100_simplifiee_Visvalingram_0_05_deg_accroche_dm_polygon_4326.shp", sep = ""))

p + geom_sf(data = zone_90_100_simplified, fill = 'yellowgreen', alpha = 0.3)

#---------------------------------------------------------------------------

Offshore_closure_z1 <- read_sf(paste(path, shapes_subfolder, "Offshore_closures/zone1.shp", sep = ""))

Offshore_closure_z2 <- read_sf(paste(path, shapes_subfolder, "Offshore_closures/zone2.shp", sep = ""))

Offshore_closure_z3 <- read_sf(paste(path, shapes_subfolder, "Offshore_closures/zone3.shp", sep = ""))

# Group the Offshore_closures into one file
Offshore_permanent_spdf <- rbind(Offshore_closure_z1, Offshore_closure_z2, Offshore_closure_z3)

p + geom_sf(data = Offshore_permanent_spdf, fill = 'yellowgreen', alpha = 0.3)

#---------------------------------------------------------------------------

Offshore_closure_seasonal <- read_sf(paste(path, shapes_subfolder, "Offshore_closures/Offshore_closure_seasonal_final.shp", sep = ""))

p + geom_sf(data = Offshore_closure_seasonal, fill = 'yellowgreen', alpha = 0.3)

```

# Create spatial points for port of calls

Because we are not interested in squares use the actual gps coords. These were pulled from:

For Grand du Roi, Sète, and Marseille:

https://latitude.to/map/fr/france/cities/ 

For all others:

https://www.toutendroit.com/en/article-le-grau-d-agde-1884412/ 
https://www.gps-latitude-longitude.com/gps-coordinates-of-port-la-nouvelle
https://www.countrycoordinate.com/city-port-de-bouc-france/

```{r main_ports}

Abbreviation <- c("GST", "XST", "CST", "GPV", "CMT", "XMA")
Name <- c("Grand-du-Roi", "Sete", "Le-Grau-d'Adge", "Port-la-Nouvelle", "Port-de-Bouc", "Marseille")
cell <- c("La43.5Lo4.1", "La43.35Lo3.6", "La43.25Lo3.4", "La43.0Lo3.05", "La43.4Lo4.9", "La43.25Lo5.35")                  
longitude <- c(4.13559, 3.69278, 3.447424, 3.043916, 4.985931, 5.38107)
latitude <- c(43.53881, 43.4028, 	43.282701, 43.021342, 43.405449, 43.29695)

Ports <- data.frame(Abbreviation, Name, cell, longitude, latitude)
head(Ports)

# convert Ports to an spatial points data.frame
Ports.wgs84 <- st_as_sf(Ports,coords = c("longitude", "latitude"), crs = st_crs(4326))

GPV.wgs84 <- subset(Ports.wgs84, Name == "Port-la-Nouvelle")
CST.wgs84 <- subset(Ports.wgs84, Name == "Le-Grau-d'Adge")
XST.wgs84 <- subset(Ports.wgs84, Name == "Sete")
GST.wgs84 <- subset(Ports.wgs84, Name == "Grand-du-Roi")
CMT.wgs84 <- subset(Ports.wgs84, Name == "Port-de-Bouc")
XMA.wgs84 <- subset(Ports.wgs84, Name == "Marseille")

```

# Create a custom theme for the map legends

```{r themes}

text_theme <- theme(axis.title = element_blank(), axis.text.y = element_text(margin=margin(t=0,r=0,b=0,l=0), size = 15), axis.text.x.bottom = element_text(margin=margin(t=0,r=0,b=0,l=0), size = 15), strip.text = element_text(size=15), panel.spacing = unit(0.35, "cm"))

```

# Create custom scales

For the spatial closure legend. 

```{r sptl.lgend.cols}

cols <- c("#003366" = str_wrap("Seasonal Offshore Extensions Applies to Gears: OTB, OTT, GNS, and LLS Seasonally (Oct-Dec) or allYear", 28),
          "#b2182b" = str_wrap("Offshore Permanent Closures Applies to Gears: OTB, OTT, GNS, LLS allYear", 28),
          "#FF33FF" = str_wrap("90-100 Isobaths Closures Applies to Gears: OTB and OTT Seasonally (Sept-Apr) or allYear", 28),
          "#614B00" = str_wrap("Northward Expansion of FRA Applies to Gears: OTB and OTT Seasonally (Nov-Apr) or allYear", 28))

cols2 <- ("#614B00" = str_wrap("Original Fishing Restricted Area [FRA] Boundaries Applies to Gears: OTB and OTT allYear", 28))

```

For the figure without a spatial closure legend.

```{r non.sptl.legend.cols}

cols3 <- c("Offshore_closure_seasonal" = "#003366",
           "Offshore_permanent_spdf" = "#b2182b",
           "zone_90_100_simplified" = "#FF33FF",
           "NewFRA_regulation" = "#614B00")

cols4 <- c("FRA" = "#614B00")

```

# Reorder the groups that we are interested in

```{r global.reorder}

EffortMetierZonesPLUS.correct2.2024 <- 
  fread(file = paste(path,'Data/EffortMetierZonesPLUS.correct2.csv', sep = ''),
        sep = ",")

EffortMetierZonesPLUS.correct_reorder <- 
  EffortMetierZonesPLUS.correct2.2024 %>% mutate(
    SceName_short =  
      recode_factor(SceName,
                  "StatusQuo"= "a",
                  "Trawler_30_Red"= "b",
                  "AllGears_30_Red" = "c",
                  "Trawler_40_Red" = "d",
                  "AllGears_40_Red"= "e",
                  "Trawler_50_Red"= "f",
                  "AllGears_50_Red"= "g",
                  "Trawler_10_20_30"= "h",
                  "AllGears_10_20_30"= "i",
                  "Trawler_10_17.5_25_32.5_40"= "j",
                  "AllGears_10_17.5_25_32.5_40"= "k",
                  "Trawler_10_20_30_40_50"= "l",
                  "AllGears_10_20_30_40_50"= "m",
                  "Original_FRA_allYear"= "n",
                  "Northward_Expansion_of_FRA_Season"= "o",
                  "Northward_Expansion_of_FRA_allYear" = "p",
                  "90-100_Isobaths_Closure_Season"= "q",
                  "90-100_Isobaths_Closure_allYear"= "r", 
                  "Offshore_Closures_Season"= "s",
                  "Offshore_Closures_allYear"= "t",
                  "Northward_Expansion_of_FRA_90-100m_Offshore_Closures_Combined"= "u",
                  "Northward_Expansion_of_FRA_Offshore_Closures_Combined" = "v",
                  "Northward_Expansion_of_FRA_90-100m_Offshore_allYear_Closures_Combined" = "w",
                  "Northward_Expansion_of_FRA_Offshore_allYear_Closures_Combined" = "x",
                  "Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_90-100m_Offshore_Closures"= "y",
                  "Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_Offshore_Closures"= "z",
                  "Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_90-100m_Offshore_Closures_allGears"= "aa",
                  "Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_Offshore_Closures_allGears"= "bb"
                ))

# View(EffortMetierZonesPLUS.correct_reorder)

```

# Create a Combined Effort map by Scenario and Year

Notes, it was decided to create two quantile scales to compare canyon and continental shelf outcomes. Subset by cell id.

## Create a Custom Secondary Palette

Required for the scale_fill_manual function.

```{r canyon.palette}

Canyon_pal <- c("#f3e6f3","#e8cce8","#d199d1","#b966b9","#a233a2","#971997","#8b008b")
pie(rep(1, 7), col = Canyon_pal)

```

## Apendix F, Figs. F.2 - F.6

Note: You will need to move the legends around to fit everything. 

```{r effort.redistribution.maps}

Continental_cells <- 
  read.csv(file = paste(path, 'Data/Continental_cells.csv', sep = ''))

Continental_cells <- unique(Continental_cells$x)

Canyon_cells <- 
  read.csv(paste(path, 'Data/Canyon_cells.csv', sep = ''))

Canyon_cells <- unique(Canyon_cells$x)

EffortAggregatedZones <- aggregate(NewEffort ~ cell + longitude + latitude + YEAR +
                                     SceName_short + SceName, data =
                                     EffortMetierZonesPLUS.correct_reorder, FUN = sum)

EffortAggregatedZones$Pop_zone <- NA

EffortAggregated_plateau <- subset(EffortAggregatedZones, cell %in% Continental_cells)

EffortAggregated_plateau$Pop_zone <- 1

EffortAggregated_canyon <- subset(EffortAggregatedZones, cell %in% Canyon_cells)

EffortAggregated_canyon$Pop_zone <- 2

EffortAggregatedZones2 <- rbind(EffortAggregated_plateau, EffortAggregated_canyon)

unique(is.na(EffortAggregatedZones2))

unique(EffortAggregatedZones2$NewEffort)

zone_effort_plots  = F

if (zone_effort_plots == FALSE){

for (s in unique(EffortAggregatedZones2$SceName)){
    effort_scen_subset <- EffortAggregatedZones2[EffortAggregatedZones2$SceName == s, ]
    print(s)

    Map_label <- unique(effort_scen_subset$SceName)
    
    # Shift so that longitude corresponds to the center of the ISIS-Fish cell
    effort_scen_subset$longitude <- effort_scen_subset$longitude + 0.025
    
    # Shift so that latitude corresponds to the center of the ISIS-Fish cell
    effort_scen_subset$latitude <- effort_scen_subset$latitude + 0.025
      
    # Create a sf object
    effort_scen_subset_wgs84 <- st_as_sf(effort_scen_subset,
                                         coords = c("longitude", "latitude"), 
                                         crs = st_crs(4326))
    # Create gridded polygon values
    effort_scen_subset_stars <- st_rasterize(effort_scen_subset_wgs84,
                                             st_as_stars(st_bbox(grid), 
                                                         values = NA_real_, 
                                                         dx = 0.05, 
                                                         dy = 0.05))
    
    effort_scen_subset_sf <- st_as_sf(effort_scen_subset_stars)
    
    effort_scen_subset_sf_shelf <- subset(effort_scen_subset_sf, 
                                          Pop_zone == 1)
    
    # get quantile breaks. Add .00001 offset to catch the lowest value
    breaks_qt_shelf <- 
      classIntervals(c(min(effort_scen_subset_sf_shelf$NewEffort) -
                         .00001, effort_scen_subset_sf_shelf$NewEffort), n = 7,
                     style = "quantile")
    
    effort_scen_subset_sf_shelf <- 
      mutate(effort_scen_subset_sf_shelf, Effort.cut_shelf = 
               cut(NewEffort, breaks_qt_shelf$brks))
    
    effort_scen_subset_sf_canyon <- subset(effort_scen_subset_sf, 
                                           Pop_zone == 2)
    
    # get quantile breaks. Add .00001 offset to catch the lowest value
    breaks_qt_canyon <- 
      classIntervals(c(min(effort_scen_subset_sf_canyon$NewEffort) -
                         .00001, effort_scen_subset_sf_canyon$NewEffort), 
                     n = 7, style = "quantile")

    effort_scen_subset_sf_canyon <- 
      mutate(effort_scen_subset_sf_canyon, Effort.cut_canyon = 
               cut(NewEffort, breaks_qt_canyon$brks))
    
    e.m.1 <- ggplot() +
      geom_sf(data = grid, color = "grey") +
      geom_sf(data = effort_scen_subset_sf_shelf, 
              aes(fill = Effort.cut_shelf), 
              color = "transparent", 
              alpha = 0.8) +
      scale_fill_brewer(name = "Zone 1",
                        palette = "Blues") +
      guides(fill=guide_legend(order = 1))+
      new_scale_fill() +
      geom_sf(data = effort_scen_subset_sf_canyon, 
              aes(fill = Effort.cut_canyon), 
              color = "transparent", alpha = 0.8) +
      scale_fill_manual(name = "Zone 2",
                        values = Canyon_pal) +
      theme_bw()+
      theme(legend.title = element_text(size = 14), legend.title.align = 0, 
            legend.text = element_text(size = 12), legend.spacing = unit(0.001, 'cm'),
            legend.position="right", legend.box = "horizontal") +
      text_theme
    
    e.m.1
    
    e.m.1.legend <- gtable_filter(ggplot_gtable(ggplot_build(e.m.1)), "guide-box") 
    
    e.m.2 <- ggplot() +
      geom_sf(data = grid, 
          color = "grey") + 
      geom_sf(data = zone_90_100_simplified,
              aes(color = "#FF33FF"),
              fill = "transparent", 
              linewidth = 0.5) +
      geom_sf_pattern(data = FRA, 
                      aes(pattern_fill = "#614B00"), 
                      pattern_fill2 = "transparent", 
                      pattern_colour = "transparent", 
                      color = "#614B00", 
                      fill = "transparent", 
                      pattern_aspect_ratio = 1.8, 
                      linewidth = 0.5, 
                      pattern_spacing = 0.01) +
      geom_sf(data = NewFRA_regulation, 
              aes(color = "#614B00"), 
              fill = "transparent", 
              linewidth = 0.5) +
      geom_sf(data = Offshore_closure_seasonal,
              aes(color = "#003366"),
              fill = "transparent", 
              linewidth = 0.25) +
      geom_sf(data = Offshore_permanent_spdf, 
              aes(color = "#b2182b"),
              fill = "transparent", 
              linewidth = 0.5) +
      scale_color_identity(name = "Closure Measures", 
                           labels = cols,
                           guide = guide_legend("color")) +
      scale_pattern_fill_identity(name = element_blank(), 
                                  labels = cols2,
                                  guide = guide_legend("pattern_fill"))+ 
      guides(color = guide_legend(order = 1),
             pattern_fill = guide_legend(order = 2)) +
      theme_bw() +
      theme(legend.title = element_blank(), legend.text = element_text(size = 12),
            legend.margin = unit(0.00, 'cm'), legend.spacing = unit(1, 'cm'),
            legend.position="left", legend.box = "vertical", legend.key.height =
              unit(1.52, 'cm'), legend.key.width = unit(1.5, 'cm')) +
      text_theme
   
    e.m.2
    
    e.m.2.legend <- gtable_filter(ggplot_gtable(ggplot_build(e.m.2)), "guide-box") 
    
    e.m.no.legend <-ggplot() +
      geom_sf(data = grid, 
              color = "grey") + 
      geom_sf(data = effort_scen_subset_sf_shelf, 
              aes(fill = Effort.cut_shelf), 
              color = "transparent", 
              alpha = 0.8) +
      scale_fill_brewer(effort_scen_subset_sf_shelf,
                        name = "Zone 1",
                        palette = "Blues") +
      guides(fill=guide_legend(order = 1))+
      new_scale_fill() +
      geom_sf(data = effort_scen_subset_sf_canyon, 
              aes(fill = Effort.cut_canyon), 
              color = "transparent", 
              alpha = 0.8) +
      scale_fill_manual(effort_scen_subset_sf_canyon,
                        name = "Zone 2", 
                        values = Canyon_pal) +
      geom_sf(data = grid, 
          color = "grey") + 
      geom_sf(data = zone_90_100_simplified,
            aes(color = "#FF33FF"),
            fill = "transparent", 
            linewidth = 0.5) +
      geom_sf_pattern(data = FRA, 
                    aes(pattern_fill = "#614B00"), 
                    pattern_fill2 = "transparent", 
                    pattern_colour = "transparent", 
                    color = "#614B00", 
                    fill = "transparent", 
                    pattern_aspect_ratio = 1.8, 
                    linewidth = 0.5, 
                    pattern_spacing = 0.01) +
      geom_sf(data = NewFRA_regulation, 
            aes(color = "#614B00"), 
            fill = "transparent", 
            linewidth = 0.5) +
      geom_sf(data = Offshore_closure_seasonal,
            aes(color = "#003366"),
            fill = "transparent", 
            linewidth = 0.25) +
      geom_sf(data = Offshore_permanent_spdf, 
              aes(color = "#b2182b"),
              fill = "transparent", 
              linewidth = 0.5) +
      scale_color_identity(name = "Closure Measures", 
                          labels = cols,
                          guide = guide_legend("color")) +
      scale_pattern_fill_identity(name = element_blank(), 
                                  labels = cols2,
                                  guide = guide_legend("pattern_fill"))+
      geom_sf(data = GDL_crop, 
              color = "#ae8f60", 
              size = 0.7, 
              fill = "#E1C699") +
      geom_sf(data = GPV.wgs84, size = 1) +
      geom_sf_text(data = GPV.wgs84, 
                   aes(label = Abbreviation),
                   size = 3.5, 
                   color = "black",
                   nudge_x = -0.02,
                   nudge_y = 0.04) +
      geom_sf(data = CST.wgs84, size = 1) +
      geom_sf_text(data = CST.wgs84, 
                   aes(label = paste0(Name, " (", Abbreviation, ")", sep = '')),
                   size = 3.5, 
                   color = "black", 
                   nudge_x = -0.18,
                   nudge_y = 0.04) +
      geom_sf(data = XST.wgs84, size = 1) +
      geom_sf_text(data = XST.wgs84, 
                   aes(label = paste0(Name, " (", Abbreviation, ")", sep = '')),
                   size = 3.5, 
                   color = "black", 
                   nudge_x = -0.10, 
                   nudge_y = 0.04) +
      geom_sf(data = GST.wgs84, size = 1) +
      geom_sf_text(data = GST.wgs84, 
                   aes(label = paste0(Name, " (", Abbreviation, ")", sep = '')),
                   size = 3.5, 
                   color = "black", 
                   nudge_x = -0.01,
                   nudge_y = 0.04) +
      geom_sf(data = CMT.wgs84, size = 1) +
      geom_sf_text(data = CMT.wgs84, 
                   aes(label = paste0(Name, " (", Abbreviation, ")", sep = '')),
                   size = 3.5, 
                   color = "black", 
                   nudge_x = 0.05,
                   nudge_y = 0.04) +
      geom_sf(data = XMA.wgs84, size = 1) +
      geom_sf_text(data = XMA.wgs84 , 
                   aes(label = paste0(Name, " (", Abbreviation, ")", sep = '')),
                   size = 3.5, 
                   color = "black", 
                   nudge_x = 0.20,
                   nudge_y = 0.04) +
      annotation_scale(location = "br", 
                       pad_x = unit(0.85, "cm"),
                       pad_y = unit(0.5, "cm"),
                       text_cex = 1,
                       tick_height = 0.9)+ 
      annotation_north_arrow(location = "tl", 
                             which_north = "true", 
                             height = unit(1, "cm"), 
                             width = unit(1, "cm"), 
                             pad_x = unit(1.25, "cm"), 
                             pad_y = unit(0.75, "cm")) +
      theme_bw()+
      theme(axis.title = element_blank(),legend.position = "none") +
      text_theme
    
    plotlegends <- arrangeGrob(e.m.1.legend, e.m.2.legend, heights = c(0.45, 0.55))
    
    plotNew <- arrangeGrob(e.m.no.legend, plotlegends, widths = c(0.67,0.33))
    
    plotNew.ggplot <- ggplotify::as.ggplot(plotNew)
    
    print(plotNew.ggplot)
    
    file.name <- paste("2024_Effort_Re-distribution- ", Map_label, sep = '')
    
    ggsave2(filename=paste(file.name,".pdf",sep=''),plot=plotNew.ggplot,device="pdf",
            path=paste(path,"Figures/",sep=""), dpi=1200, width = 29.7, height=17,
            unit="cm",
                      limitsize = FALSE)
    
      }
  }

```