---
title: "MEDISIS Values OtherSpecies.Rmd"
author: "Stephanie Hopkins"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: yes
---

STOP!!!

In order to run this code you must first have the following files:

1) "EffNomtot_6.4_without-0s.csv"
2) "EffNomtot_6.4_true_0s.csv"
2) "Final_VPUEs.csv" These are the 2017 values

A ReadMe.txt file has been created to help facilitate the work flow you should take.

# Setup paths, data, and libraries

```{r setup, include=FALSE}

rm(list=ls())

knitr::opts_chunk$set(echo = TRUE, message=FALSE, results = "hide")

list.of.packages <- c("data.table","tidyverse","reshape2")

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

library(reshape2)
library(data.table)
library(tidyverse)

# To Replace with your file directory
dir <- "C:/Users/steph/Documents"

MEDISIS <- "/MEDISIS/Part2.Analysing.the.simulation.output/"

path <- paste(dir,MEDISIS,sep="")

```

# Load Only Nominal Effort

```{r effort}

name_RData_6.4_effort <- 'EffNomtot_6.4_without-0s'
EffNomtot_6.4 <- fread(paste(path, "Data/", name_RData_6.4_effort,'.csv',sep = ''))

nameRDATA_clean <- 'EffNomtot_6.4_true_0s'
EffNomtot_6.4_matched <- fread(paste(path, "Data/", nameRDATA_clean, '.csv', sep = ''))

EffNomtot_6.4 <- rbind(EffNomtot_6.4, EffNomtot_6.4_matched)

rm(EffNomtot_6.4_matched)

```

# Join the simulation design table to the simulation output

Apply the names of the Scenarios in the column designating their numeric values and graft this to the Data.

```{r simulation.bind}

simuDesign <- '/MEDISIS/Part1.Reproducing.the.simulation.data/ISIS.Fish.Input.Tables/simulation_design_28'

simulationDesign <- fread(paste(dir, simuDesign,".csv", sep=""), sep=';', h=F)

colnames(simulationDesign) =  c('InitialAbundance','Recruitment','Connectivity','Scenarios')

simulationDesign$simu <- seq(0, 503, 1)

step <- unique(EffNomtot_6.4$step)
nbYear <- length(step)/12 
YEAR <- sort(rep(seq(2015,2014+nbYear,1), 12))
MONTH <- rep(seq(1,12,1),nbYear)
tabStep <- data.frame(step, YEAR, MONTH)

EffNomtot_6.4 <- inner_join(EffNomtot_6.4, tabStep, by=c('step'))
EffNomtot_6.4 <- inner_join(EffNomtot_6.4, simulationDesign, by=c('simu'))

table_Sce_6.4 <- data.frame(Scenarios=as.character(c(0:27)),SceName=c("StatusQuo","Trawler_30_Red","Trawler_40_Red","Trawler_50_Red","Trawler_10_20_30","Trawler_10_17.5_25_32.5_40","Trawler_10_20_30_40_50","AllGears_30_Red","AllGears_40_Red","AllGears_50_Red","AllGears_10_20_30","AllGears_10_17.5_25_32.5_40","AllGears_10_20_30_40_50","Original_FRA_allYear","Northward_Expansion_of_FRA_Season","Northward_Expansion_of_FRA_allYear","90-100_Isobaths_Closure_Season","90-100_Isobaths_Closure_allYear","Offshore_Closures_Season","Offshore_Closures_allYear","Northward_Expansion_of_FRA_90-100m_Offshore_Closures_Combined","Northward_Expansion_of_FRA_90-100m_Offshore_allYear_Closures_Combined","Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_90-100m_Offshore_Closures","Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_90-100m_Offshore_Closures_allGears","Northward_Expansion_of_FRA_Offshore_Closures_Combined","Northward_Expansion_of_FRA_Offshore_allYear_Closures_Combined","Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_Offshore_Closures","Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_Offshore_Closures_allGears"))

```

# Filter data

Note that while we parameterise OTB_XST_18-24 and OTM_CMT_18-24 in ISIS-Fish, these are not active metier or they do not target hake.

```{r drop.inactive.metier}

EffNomtot_6.4 <- subset(EffNomtot_6.4, !metier %in% c("OTB_XST_18-24","OTM_CMT_18-24"))

dim(EffNomtot_6.4)
# [1] 1935360  11

```

# Combine all values into a single data table

This part is broken into several smaller steps, but essentially we want to merge observation data and simplify the nominal effort data. Calculate the total catch size and aggregate.

```{r nominal.effort.table}

# For Nominal Effort by métier:
effort_yearmon_metier <- setNames(aggregate(value~metier+YEAR+MONTH+simu+InitialAbundance+Recruitment+Connectivity+Scenarios,data=EffNomtot_6.4,sum),c("METIER","YEAR","MONTH","simu","InitialAbundance","Recruitment","Connectivity","Scenarios","Nominal_Effort"))

#View(effort_year_metier)

effort_yearmon_metier <- merge(effort_yearmon_metier, table_Sce_6.4, by = c("Scenarios"), all.x = TRUE)

effort_check1 <- subset(effort_yearmon_metier, InitialAbundance == 0 & Recruitment == 0 & Connectivity == 0 & Scenarios == 16 & YEAR %in% c(2020, 2024))

effort_check1.1 <- aggregate(Nominal_Effort ~ YEAR + MONTH + METIER, 
                             data = effort_check1, FUN = sum, 
                             na.action = na.omit)

dim(effort_check1.1)
# [1] 552   4

```

# Create a second metier id to join VPUE on

We need a year month unique value per scenario groups, which utilizes specific VPUE metier ids to match scenarios with SceName.

Assign original FRA scenarios:

```{r second.met.FRA}

effort_yearmon_metier_fra <- effort_yearmon_metier %>%
  filter(SceName == "Original_FRA_allYear", YEAR > 2019)

effort_yearmon_metier_fra$METIER2 <- 
  paste(effort_yearmon_metier_fra$METIER, "_FRA", sep="")

summary(effort_yearmon_metier_fra)

```

Assign northward expansion of FRA - seasonal scenarios:

```{r second.met.NW.Expan.FRA.seas}

effort_yearmon_metier_newfra.se <- effort_yearmon_metier %>%
  filter(SceName == "Northward_Expansion_of_FRA_Season", YEAR > 2019)

effort_yearmon_metier_newfra.se$METIER2 <- paste(effort_yearmon_metier_newfra.se$METIER, "_newFRA.reg.se", sep="")

```

Assign northward expansion of FRA - permanent scenarios:

```{r second.met.NW.Expan.FRA.perm}

effort_yearmon_metier_newfra.yr <- effort_yearmon_metier %>%
  filter(SceName == "Northward_Expansion_of_FRA_allYear", YEAR > 2019)

effort_yearmon_metier_newfra.yr$METIER2 <- paste(effort_yearmon_metier_newfra.yr$METIER, "_newFRA.reg.yr", sep="")

```

Assign 90-100m isobath closure - seasonal scenarios:

```{r second.met.90.100m.iso.seas}

effort_yearmon_metier_iso_se <- effort_yearmon_metier %>%
  filter(SceName == "90-100_Isobaths_Closure_Season", YEAR > 2019)

effort_yearmon_metier_iso_se$METIER2 <- paste(effort_yearmon_metier_iso_se$METIER, "_iso.se", sep="")

```

Assign 90-100m isobath closure - permanent scenarios:

```{r second.met.90.100m.iso.perm}

effort_yearmon_metier_iso_yr <- effort_yearmon_metier %>%
  filter(SceName == "90-100_Isobaths_Closure_allYear", YEAR > 2019)

effort_yearmon_metier_iso_yr$METIER2 <- paste(effort_yearmon_metier_iso_yr$METIER, "_iso.yr", sep="")

```

Assign offshore closure - seasonal scenarios:

Recall this is a network of three permanent closure sites and a seasonal extension that is added from October 15th to December 15th. 

```{r offshore.closure.seas}

effort_yearmon_metier_offshore_se <- effort_yearmon_metier %>%
  filter(SceName == "Offshore_Closures_Season", YEAR > 2019)

effort_yearmon_metier_offshore_se$METIER2 <- paste(effort_yearmon_metier_offshore_se$METIER, "_offshore.se", sep="")

```

Assign offshore closure - seasonal scenarios:

Recall this is a network of three permanent closure sites, we change the seasonal extension to a permanent expansion. 

```{r offshore.closure.perm}

effort_yearmon_metier_offshore_yr <- effort_yearmon_metier %>%
  filter(SceName == "Offshore_Closures_allYear", YEAR > 2019)

effort_yearmon_metier_offshore_yr$METIER2 <- paste(effort_yearmon_metier_offshore_yr$METIER, "_offshore.yr", sep="")

```

Assign combined spatial closure network with isobath - seasonal scenarios:

```{r csptl.network.w.iso.seas}

effort_yearmon_metier_csptl.w.iso.se <- effort_yearmon_metier %>%
  filter(SceName == "Northward_Expansion_of_FRA_90-100m_Offshore_Closures_Combined", YEAR > 2019)

effort_yearmon_metier_csptl.w.iso.se$METIER2 <- paste(effort_yearmon_metier_csptl.w.iso.se$METIER, "_csptl.w.iso.se", sep="")

```

Assign combined spatial closure network without 90-100m isobath closure - seasonal scenarios:

```{r csptl.network.wo.iso.seas}

effort_yearmon_metier_csptl.wo.iso.se <- effort_yearmon_metier %>%
  filter(SceName == "Northward_Expansion_of_FRA_Offshore_Closures_Combined",
         YEAR > 2019)

effort_yearmon_metier_csptl.wo.iso.se$METIER2 <- paste(effort_yearmon_metier_csptl.wo.iso.se$METIER, "_csptl.wo.iso.se", sep="")

```

Assign combined spatial closure network with isobath - permanent scenarios:

```{r csptl.network.w.iso.perm}

effort_yearmon_metier_csptl.w.iso.yr <- effort_yearmon_metier %>%
  filter(SceName == "Northward_Expansion_of_FRA_90-100m_Offshore_allYear_Closures_Combined", YEAR > 2019)

effort_yearmon_metier_csptl.w.iso.yr$METIER2 <- paste(effort_yearmon_metier_csptl.w.iso.yr$METIER, "_csptl.w.iso.yr", sep="")

```

Assign combined spatial closure network without 90-100m isobath closure - permanent scenarios:

```{r csptl.network.wo.iso.perm}

effort_yearmon_metier_csptl.wo.iso.yr <- effort_yearmon_metier %>%
  filter(SceName == "Northward_Expansion_of_FRA_Offshore_allYear_Closures_Combined", YEAR > 2019)

effort_yearmon_metier_csptl.wo.iso.yr$METIER2 <- paste(effort_yearmon_metier_csptl.wo.iso.yr$METIER, "_csptl.wo.iso.yr", sep="")

```

Assign effort reduction and combined spatial closure network with 90-100m isobath closure - seasonal scenarios:

```{r effort.red.csptl.network.w.iso.perm}

effort_French_metier_spatial_scenarios_w.iso <- c("Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_90-100m_Offshore_Closures",
"Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_90-100m_Offshore_Closures_allGears")

effort_yearmon_metier_effort.csptl.w.iso <- effort_yearmon_metier %>%
  filter(SceName %in% effort_French_metier_spatial_scenarios_w.iso, YEAR > 2019)

effort_yearmon_metier_effort.csptl.w.iso$METIER2 <- paste(effort_yearmon_metier_effort.csptl.w.iso$METIER, "_effort.csptl.w.iso", sep="")

```

Assign effort reduction and combined spatial closure network without 90-100m isobath closure - seasonal scenarios:

```{r effort.red.csptl.network.wo.iso.perm}

effort_yearmon_metier_spatial_scenarios_wo.iso <- c("Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_Offshore_Closures",
"Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_Offshore_Closures_allGears")

effort_yearmon_metier_effort.csptl.wo.iso <- effort_yearmon_metier %>% filter(SceName %in% effort_yearmon_metier_spatial_scenarios_wo.iso, YEAR > 2019)

effort_yearmon_metier_effort.csptl.wo.iso$METIER2 <- paste(effort_yearmon_metier_effort.csptl.wo.iso$METIER, "_effort.csptl.wo.iso", sep="")

```

# Filter out all non-spatial scenario metiers

For these you will need to match on METIER, YEAR, MONTH.

```{r non.sptl.closure.scen}

effort_yearmon_metier_nonsptl_scenarios <- c("StatusQuo","Trawler_30_Red","Trawler_40_Red","Trawler_50_Red","Trawler_10_20_30","Trawler_10_17.5_25_32.5_40","Trawler_10_20_30_40_50","AllGears_30_Red","AllGears_40_Red","AllGears_50_Red","AllGears_10_20_30","AllGears_10_17.5_25_32.5_40","AllGears_10_20_30_40_50")

effort_yearmon_metier_nonsptl.pt1 <- effort_yearmon_metier %>%
  filter(SceName %in% effort_yearmon_metier_nonsptl_scenarios) 

effort_yearmon_metier_nonsptl.pt2 <- effort_yearmon_metier %>%
  filter(!SceName %in% effort_yearmon_metier_nonsptl_scenarios, YEAR < 2020)

summary(effort_yearmon_metier_nonsptl.pt2)

effort_yearmon_metier_nonsptl <- rbind(effort_yearmon_metier_nonsptl.pt1, effort_yearmon_metier_nonsptl.pt2)

effort_yearmon_metier_nonsptl$METIER2 <- effort_yearmon_metier_nonsptl$METIER

```

# Merge all data frames with renamed metier

```{r join.met2.data}

effort_yearmon_metier.pt1 <- rbind(
  effort_yearmon_metier_fra,
  effort_yearmon_metier_newfra.se, 
  effort_yearmon_metier_newfra.yr, 
  effort_yearmon_metier_iso_se, 
  effort_yearmon_metier_iso_yr, 
  effort_yearmon_metier_offshore_se, 
  effort_yearmon_metier_offshore_yr, 
  effort_yearmon_metier_csptl.w.iso.se, 
  effort_yearmon_metier_csptl.w.iso.yr, 
  effort_yearmon_metier_effort.csptl.w.iso, 
  effort_yearmon_metier_csptl.wo.iso.se, 
  effort_yearmon_metier_csptl.wo.iso.yr, 
  effort_yearmon_metier_effort.csptl.wo.iso, 
  effort_yearmon_metier_nonsptl)

dim(effort_yearmon_metier.pt1)
# [1] 1391040  11

dim(distinct(effort_yearmon_metier.pt1))
# [1] 1391040  11

unique(effort_yearmon_metier.pt1$METIER2)
# 504 metiers to match

unique(effort_yearmon_metier.pt1$METIER)

# Create an ID based on scenario context
effort_yearmon_metier.pt1$combisim <- paste0("Init",effort_yearmon_metier.pt1$InitialAbundance,"_Recr",effort_yearmon_metier.pt1$Recruitment,"_Conn",effort_yearmon_metier.pt1$Connectivity,"_Scen",effort_yearmon_metier.pt1$Scenarios)

length(unique(effort_yearmon_metier.pt1$combisim))
# 504 entries

View(effort_yearmon_metier.pt1)

```

# Replicate Effort to match each taxon and add taxon column

```{r extend.data}

# Replicate effort data
effort_yearmon_metier.pt2 <- unique(effort_yearmon_metier.pt1) %>% 
  slice(rep(1:n(), 10))

# View(effort_yearmon_metier.pt2)

dim(effort_yearmon_metier.pt2)
# [1] 13910400  12

species.list <- c("Solea solea", "Illex spp.", "Loliginidae", "Mullus spp.",
                  "Scomber scombrus", "Lophius spp.", "Trisopterus minutus",
                  "Octopus vulgaris and Eledone spp.",
                  "Engraulis encrasicolus", "Others")

# Create taxon list to fill vector 13910400/10 = 1391040
effort_yearmon_metier.pt2$TAXON_GROUP_NAME <- rep(species.list, each =  1391040)

colnames(effort_yearmon_metier.pt2)

# View(effort_yearmon_metier.pt2)

# Check for NA values
unique(is.na(effort_yearmon_metier.pt2))

unique(effort_yearmon_metier.pt2$METIER)

unique(effort_yearmon_metier.pt2$METIER2)

```

# Load VPUE data 

Note there is a problem with the data join and even still the revenues in the data set are lower than the GFCM values. 

```{r vpue}

Final_VPUEs <- read.csv(paste(path, 'Data/Revenues/Final_VPUEs.csv', sep=""),
                        sep = ";")

unique(Final_VPUEs$TAXON_GROUP_NAME)

Final_VPUEs <- subset(Final_VPUEs, !TAXON_GROUP_NAME == "Merluccius merluccius")

dim(Final_VPUEs)
# [1] 236534  5

Final_VPUEs.distinct <- distinct(Final_VPUEs)

dim(Final_VPUEs.distinct)
# [1] 236534  5

head(Final_VPUEs.distinct)

unique(Final_VPUEs.distinct$METIER)

names(Final_VPUEs.distinct)[3] <- "METIER2"

# For all metier except those with GNS_FRA in the character string
Final_VPUEs.distinct.excludeGNS <- Final_VPUEs.distinct %>%
  filter (!grepl('GNS_FRA', METIER2))

unique(Final_VPUEs.distinct.excludeGNS$METIER)

Final_VPUEs.distinct.excludeGNS$METIER <-
  substr(Final_VPUEs.distinct.excludeGNS$METIER2, 1, 13)

unique(Final_VPUEs.distinct.excludeGNS$METIER)

# For all metier with GNS_FRA in the character string
Final_VPUEs.distinct.GNS <- Final_VPUEs.distinct %>%
  filter (grepl('GNS_FRA', METIER2))

unique(Final_VPUEs.distinct.GNS$METIER2)

Final_VPUEs.distinct.GNS$METIER <- substr(Final_VPUEs.distinct.GNS$METIER2, 1, 7)

unique(Final_VPUEs.distinct.GNS$METIER)

Final_VPUEs.w_Metier <- 
  rbind(Final_VPUEs.distinct.excludeGNS, Final_VPUEs.distinct.GNS)

```

# Check for outliers

```{r oulier.check}

Final_VPUE_metier.list <- unique(Final_VPUEs.w_Metier$METIER2)
Final_VPUE_metier.list

effort_yearmon_metier.pt2.nomatch <- effort_yearmon_metier.pt2 %>%
  filter(!METIER2 %in% Final_VPUE_metier.list)

unique(effort_yearmon_metier.pt2.nomatch$METIER2)

```

# Join data sets

```{r vpue.plus.met2.data.frame}

effort_year_metier_vpue_taxon <- left_join(effort_yearmon_metier.pt2,
                                           Final_VPUEs.w_Metier, 
                                           by = c("YEAR", "MONTH", "METIER",
                                                  "METIER2", "TAXON_GROUP_NAME"))

dim(effort_year_metier_vpue_taxon)
# [1] 17663760  14

# View(effort_year_metier_vpue_taxon)

effort_year_metier_vpue_taxon_distinct <- distinct(effort_year_metier_vpue_taxon)

dim(effort_year_metier_vpue_taxon_distinct)
# [1] 17663760  14

unique(is.na(effort_year_metier_vpue_taxon_distinct))

# Recode na VPUE as 0
effort_year_metier_vpue_taxon_distinct$VPUE[is.na(effort_year_metier_vpue_taxon_distinct$VPUE)] <- 0

range(effort_year_metier_vpue_taxon_distinct$VPUE)

unique(is.na(effort_year_metier_vpue_taxon_distinct))

```

# Check outputs

```{r check.join}

check_VPUE_test1 <- filter(effort_year_metier_vpue_taxon_distinct, YEAR %in% c(2020, 2024) & combisim == "Init0_Recr0_Conn0_Scen3")

check_VPUE_test1

# VPUE should be the same between years
check_VPUE_test2 <- aggregate(VPUE ~ YEAR + TAXON_GROUP_NAME, data = check_VPUE_test1, sum, na.action = na.omit)

check_VPUE_test2

# Effort should be identical
check_VPUE_test3 <- aggregate(Nominal_Effort ~ YEAR + TAXON_GROUP_NAME, data = check_VPUE_test1, sum, na.action = na.omit)

check_VPUE_test3

# View(effort_year_metier_vpue_taxon)

```

# Calculate revenues

Aggregations will be handled in a separate file: *MEDITS.Revenues.bySpecies.Rmd*.

```{r revenue.values}

effort_year_metier_vpue_taxon_distinct$Revenues <-
  effort_year_metier_vpue_taxon_distinct$Nominal_Effort *
  effort_year_metier_vpue_taxon_distinct$VPUE

unique(is.na(effort_year_metier_vpue_taxon_distinct))

```

# Explore and save the data

```{r explore.revenues}

pathRData_6.4 <- 'Data/' 

save(effort_year_metier_vpue_taxon_distinct, 
     file = paste(path, pathRData_6.4, 'effort_year_metier_vpue_taxon_distinct', '.RData', sep=''))

check_revenues <- filter(effort_year_metier_vpue_taxon_distinct, 
                         YEAR == 2017 & combisim == "Init0_Recr0_Conn0_Scen0")

check_revenues <- sum(check_revenues$Revenues)
check_revenues
# [1] 25914435

check_revenues2 <- filter(effort_year_metier_vpue_taxon_distinct,
                          YEAR %in% c(2020, 2024) & combisim ==
                            "Init0_Recr0_Conn0_Scen16")

check_revenues2 <- aggregate(Revenues ~ YEAR + TAXON_GROUP_NAME, 
                             data = check_revenues2, FUN = sum, 
                             na.action = na.omit)

check_revenues2

check_revenues3 <- check_revenues2 %>%
  filter(YEAR == 2020)

sum(check_revenues3$Revenues)
# [1] 25430622

```

