---
title: "Spider.plots.main.14"
author: "Stephanie Hopkins"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
---

```{r setup, include=FALSE}

rm(list = ls())
gc()

knitr::opts_chunk$set(echo=TRUE)
knitr::opts_chunk$set(message=FALSE)


list.of.packages <- c("data.table","tidyverse","fmsb","scales")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

library(data.table)
library(fmsb)
library(tidyverse)
library(scales)

# To Replace with your file directory
# dir <- "D:/steph/Documents"
dir <- "C:/Users/shopkins/Desktop"

MEDISIS <- "/MEDISIS/Part2.Analysing.the.simulation.output/"

path <- paste(dir,MEDISIS,sep="")

```

# Load the datasets

Prep the data for year 5 catch by fleet

```{r}

fleet.catch <- fread(paste(path,"Data/",
                           "fleet.catch.weight.by.year.csv", sep=''), sep=";")

head(fleet.catch)

fleet.catch.prestep <- fleet.catch %>% 
  filter(YEAR == 2024 & !SceName_short %in%
           c("b","c","f","g","h","i","l","m","s","t","v","x","z","bb")) %>%
  select(Scenarios, SceName, Scenario_type, SceName_short, Rel_Diff_wg, fleet) %>%
  mutate(Rel_Diff_wg = round(Rel_Diff_wg)) %>% 
  distinct()

head(fleet.catch.prestep)

```

## Subset the data

For first index: French trawlers

```{r French.trawl.catch, echo=TUE}

French.trawlers.yr5 <- fleet.catch.prestep %>%
  filter(fleet == "French Trawlers")

# Create a unique index names
names(French.trawlers.yr5)[5] <- "French.trawl.catch"

# remove fleet column
French.trawlers.yr5 <- French.trawlers.yr5[,-6]

```

For second index: French gillnetters

```{r French.gillnetter.catch, echo=TRUE}

French.gillnetters.yr5 <- fleet.catch.prestep %>%
  filter(fleet == "French Gillnetters")

# Create a unique index names
names(French.gillnetters.yr5)[5] <- "French.gillnetter.catch"

# remove fleet column
French.gillnetters.yr5 <- French.gillnetters.yr5[,-6]

```

For third index: Spanish trawlers

```{r Spanish.trawler.catch, echo=TRUE}

Spanish.trawlers.yr5 <- fleet.catch.prestep %>%
  filter(fleet == "Spanish Trawlers")

# Create a unique index names
names(Spanish.trawlers.yr5)[5] <- "Spanish.trawler.catch"

# remove fleet column
Spanish.trawlers.yr5 <- Spanish.trawlers.yr5[,-6]

```

For fourth index: Spanish longliners

```{r Spanish.longliners.catch, echo=TRUE}

Spanish.longliners.yr5 <- fleet.catch.prestep %>%
  filter(fleet == "Spanish longliners")

# Create a unique index names
names(Spanish.longliners.yr5)[5] <- "Spanish.longliners.catch"

# remove fleet column
Spanish.longliners.yr5 <- Spanish.longliners.yr5[,-6]

```

# Load the biomass data set

Prep the data for year 5 biomass by zone

```{r biomass.data.prep year5, echo=TRUE}

zone.biomass <- fread(paste(path,"/Data/",
                            "biomass.zone.by.year.csv", sep=''), sep=";")

head(zone.biomass)

biomass.recovery <- zone.biomass %>% 
  filter(YEAR == 2024 & !SceName_short %in% 
           c("b","c","f","g","h","i","l","m","s","t","v","x","z","bb")) %>%
  select(Scenarios, SceName, Scenario_type, SceName_short, Rel_Diff_biom, ZONE) %>%
  mutate(Rel_Diff_biom = round(Rel_Diff_biom))

head(biomass.recovery)

```

## Subset the data

For fifth index: biomass recovery continental shelf

```{r shelf.biomass, echo=TRUE}

shelf.biomass.yr5 <- biomass.recovery %>%
  filter(ZONE == "Zone 1")

head(shelf.biomass.yr5)

# Create a unique index names
names(shelf.biomass.yr5)[5] <- "shelf.biomass"

# Remove zone column
shelf.biomass.yr5 <- shelf.biomass.yr5[,-6]

```

For sixth index: biomass recovery continental slope interface

```{r slope.interface.biomass, echo=TRUE}

interface.biomass.yr5 <- biomass.recovery %>%
  filter(ZONE == "Zone 2")

head(interface.biomass.yr5)

# Create a unique index names
names(interface.biomass.yr5)[5] <- "slope.interface.biomass"

# Remove zone column
interface.biomass.yr5 <- interface.biomass.yr5[,-6]

```

# Format the data for the spider charts

Join data sets

```{r joined.set, echo=TRUE}

index_values <- inner_join(French.trawlers.yr5, French.gillnetters.yr5) 
unique(index_values$SceName_short)
colnames(index_values)

index_values2 <- inner_join(index_values, Spanish.trawlers.yr5)
unique(index_values2$SceName_short)
colnames(index_values2)

index_values3 <- inner_join(index_values2, Spanish.longliners.yr5) 
unique(index_values3$SceName_short)
colnames(index_values3)

index_values4 <- inner_join(index_values3, shelf.biomass.yr5) 
unique(index_values4$SceName_short)
colnames(index_values4)

index_values5 <- inner_join(index_values4, interface.biomass.yr5) %>%
  distinct() 

unique(index_values5$SceName_short)

colnames(index_values5)

# View(index_values5)

```

##  Creat custom function 

code found at: https://www.datanovia.com/en/blog/beautiful-radar-chart-in-r-using-fmsb-and-ggplot-packages/#key-function-and-arguments

```{r radarchart.fun, echo=TRUE}

create_beautiful_radarchart <- function(data, color = "#00AFBB", 
                                        vlabels = colnames(data), vlcex = 1,
                                        caxislabels = NULL, title = NULL, ...){
  radarchart(
    data, axistype = 1,
    # Customize the polygon
    pcol = color, pfcol = scales::alpha(color, 0.5), plwd = 2, plty = 1,
    # Customize the grid
    cglcol = "darkgrey", cglty = 1, cglwd = 0.8,
    # Customize the axis
    axislabcol = "black", 
    # Variable labels
    vlcex = vlcex, vlabels = vlabels,
    caxislabels = caxislabels, title = title, ...
  )
}

```

## Reorder the data

```{r reorder.dat, echo=TRUE}

# in order to use the library fmsb, the data must be a data frame
index_values.df2 <- as.data.frame(index_values5)

# in order to use the library fmsb, you must name the rows
row.names(index_values.df2) <- index_values.df2$SceName

unique(index_values.df2$SceName)

# View(index_values.df2)

sort(index_values.df2$SceName_short)

plot.order <- c("a", "d", "e", "j", "k", "n", "o", "p", "q", "r", "u", "w", "y", "aa")

index_values.df2 <- index_values.df2 %>% 
  arrange(SceName_short) %>% 
  mutate(plot.order = c(1,14,seq(2,13,1))) %>%
  arrange(plot.order)

# View(index_values.df2)

index_values.df3 <- index_values.df2[,-c(1:4,11)]

# View(index_values.df3)

# Make names prettier
names(index_values.df3) <- c("French trawl catch", "French gillnetter catch", "Spanish trawler catch", "Spanish.longliners.catch", "shelf biomass", "slope interface biomass")

```

## Recale the data from 0 to 1

```{r rescale, echo=TRUE}}

index_values.df3_scaled <- round(apply(index_values.df3, 2, scales::rescale), 2)

index_values.df3_scaled <- as.data.frame(index_values.df3_scaled)

# View(index_values.df3_scaled)

```

## Create variables summary

```{r summary.var, echo=TRUE}

# Get the minimum and the max of every column  
col_max <- apply(index_values.df3_scaled, 2, max)
col_min <- apply(index_values.df3_scaled, 2, min)

# Calculate the average profile 
col_mean <- apply(index_values.df3_scaled, 2, mean)

# Put together the summary of columns
col_summary <- t(data.frame(Max = col_max, Min = col_min, Average = col_mean))

# Bind variables summary to the data
index_values.df3_scaled <- as.data.frame(rbind(col_summary, index_values.df3_scaled))

head(index_values.df3_scaled)

```

## Shorten names

```{r short.name, echo=TRUE}

index_values.df3_scaled.short <- index_values.df3_scaled
rownames(index_values.df3_scaled.short) <- 
  c("Max",        "Min",        "Average",    "Status Quo", "Scenario d", 
    "Scenario e", "Scenario j", "Scenario k", "Scenario n", "Scenario o", 
    "Scenario p", "Scenario q", "Scenario r", "Scenario u", "Scenario w",  
    "Scenario y", "Scenario aa")

```

## Plot scenrio outputs

```{r Fig.6, echo=TRUE}

opar <- par() 

# Define settings for plotting in a 3x4 grid, with appropriate margins:
par(mar = rep(0.8,4))
par(mfrow = c(4,4))

# Produce a radar-chart for each student
for (i in 4:nrow(index_values.df3_scaled.short)) {
  radarchart(
    index_values.df3_scaled.short[c(1:3, i), ],
    pfcol = c("#99999980",NA),
    pcol= c(NA,2), plty = 1, plwd = 2,
    title = row.names(index_values.df3_scaled.short)[i]
  )
}

# Restore the standard par() settings
par <- par(opar) 

```
