---
title: "MEDISIS Catch Weight and Catch Weight by Metier"
author: "Stephanie Hopkins"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: yes
---

```{r setup, include=FALSE, fig.width=6, fig.height=6}

rm(list = ls())
gc()

knitr::opts_chunk$set(echo=TRUE, message=FALSE, results = "hide")

list.of.packages <- c("data.table","tidyverse")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

library(data.table)
library(tidyverse)

# To Replace with your file directory
dir <- "C:/Users/steph/Documents"

MEDISIS <- "/MEDISIS/Part2.Analysing.the.simulation.output/"

path <- paste(dir,MEDISIS,sep="")

```

# Make your life easy and save custom themes

```{r custom.theme, echo=TRUE}

bar_chart_text_theme <- theme(axis.title.x = element_text(margin=margin(t=5,r=0,b=0,l=0), size = 14), axis.text.y = element_text(margin=margin(t=0,r=1,b=0,l=0), size = 12), axis.text.x.bottom = element_text(margin=margin(t=1,r=0,b=0,l=0), size = 12), axis.title.y = element_text(size = 14), strip.text = element_text(size=12), panel.spacing = unit(0.5, "cm")) 

bar_chart_legend_theme <- theme(legend.title = element_blank(), legend.text = element_text(size = 12),legend.text.align = 0, legend.direction = "horizontal", legend.spacing = unit(0.001, 'cm'), legend.key.height = unit(1.52, 'cm'), legend.key.width = unit(1.5, 'cm'), legend.position="bottom")

```

# Create a custom colour palette

Now that we are satisfied with the groupings, create a custom colour palette that matches colours with the: 2nd and 4th 3rd and 5th 7th and 8th 9th and 10th values.

```{r colour.pallete, echo=TRUE}

c_rel_diff <- c("#000000", #BLACK
                "#0492C2", #CERULEAN
                "#78C0f0", #SKY
                "#008081", #TEAL
                "#4F97A3", #TURKISH BLUE
                "#CC9966", #TAN
                "#a67556", #Brown
                "#3DED97", #SEAFOAM
                "#99EDC3", #MINT
                "#32612D", #BASIL
                "#597D35" #PICKLE
) 

#pie(rep(1, 11), col = c_rel_diff)

```

# Adjust the plot order

```{r break.list, echo=TRUE}

breaks_list <- c(
  "StatusQuo",
  "All-at-once Trawler Effort Reduction",
  "All-at-once Effort Reduction Applied to All Gears",
  "Gradual Trawler Effort Reduction",
  "Gradual Effort Reduction Applied to All Gears",
  "Seasonal Spatial Closure Single Effects",
  "Annual Spatial Closure Single Effects",
  "With 90-100m Isobaths Spatial Closure Combined Effects",
  "Without 90-100m Isobaths Spatial Closure Combined Effects",
  "Spatial Closure and Effort Reduction Combined Effects With the 90-100m Isobaths Closure",
  "Spatial Closure and Effort Reduction Combined Effects Without the 90-100m Isobaths Closure")

```

# Load only catch weight

```{r catch.weight, echo=TRUE}

# 15706980 entries
name_RData_6.4 <- 'catchWgtot_6.4_without-0s'

catchWgtot_6.4 <- fread(paste(path, "Data/", name_RData_6.4,'.csv',sep=''))

dim(catchWgtot_6.4)
# [1] 14724396  8

nameRDATA_clean <- 'catchWgtot_6.4_true_0s'

catchWgtot_6.4_matched <-fread(paste(path, "Data/", nameRDATA_clean,'.csv',sep=''))

dim(catchWgtot_6.4_matched)
# [1] 9951444 8

catchWgtot_6.4 <- rbind(catchWgtot_6.4, catchWgtot_6.4_matched)

rm(catchWgtot_6.4_matched)

```

# Join the simulation design table to the simulation output

Apply the names of the Scenarios in the column designating their numeric values and graft this to the Data.

```{r simulation.bind, echo=TRUE}

simuDesign <- '/MEDISIS/Part1.Reproducing.the.simulation.data/ISIS.Fish.Input.Tables/simulation_design_28'

simulationDesign <- fread(paste(dir, simuDesign,".csv", sep=""), sep=';', h=F)

colnames(simulationDesign) =  c('InitialAbundance','Recruitment','Connectivity','Scenarios')

simulationDesign$simu <- seq(0, 503, 1)

step <- unique(catchWgtot_6.4$step)
nbYear <- length(step)/12 
YEAR <- sort(rep(seq(2015,2014+nbYear,1), 12))
MONTH <- rep(seq(1,12,1),nbYear)
tabStep <- data.frame(step, YEAR, MONTH)

catchWgtot_6.4 <- inner_join(catchWgtot_6.4, tabStep, by=c('step'))
catchWgtot_6.4 <- inner_join(catchWgtot_6.4, simulationDesign, by=c('simu'))

table_Sce_6.4 <- data.frame(Scenarios=as.character(c(0:27)),SceName=c("StatusQuo","Trawler_30_Red","Trawler_40_Red","Trawler_50_Red","Trawler_10_20_30","Trawler_10_17.5_25_32.5_40","Trawler_10_20_30_40_50","AllGears_30_Red","AllGears_40_Red","AllGears_50_Red","AllGears_10_20_30","AllGears_10_17.5_25_32.5_40","AllGears_10_20_30_40_50","Original_FRA_allYear","Northward_Expansion_of_FRA_Season","Northward_Expansion_of_FRA_allYear","90-100_Isobaths_Closure_Season","90-100_Isobaths_Closure_allYear","Offshore_Closures_Season","Offshore_Closures_allYear","Northward_Expansion_of_FRA_90-100m_Offshore_Closures_Combined","Northward_Expansion_of_FRA_90-100m_Offshore_allYear_Closures_Combined","Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_90-100m_Offshore_Closures","Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_90-100m_Offshore_Closures_allGears","Northward_Expansion_of_FRA_Offshore_Closures_Combined","Northward_Expansion_of_FRA_Offshore_allYear_Closures_Combined","Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_Offshore_Closures","Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_Offshore_Closures_allGears"))

```

# Filter data

Note that while we parameterise OTB_XST_18-24 and OTM_CMT_18-24 in ISIS-Fish, these are not active metier or they do not target hake.

```{r drop.inactive.metier, echo=TRUE}

test.met <- subset(catchWgtot_6.4, metier %in% c("OTB_XST_18-24","OTM_CMT_18-24"))

catchWgtot_6.4 <- subset(catchWgtot_6.4, !metier %in% c("OTB_XST_18-24","OTM_CMT_18-24"))

dim(catchWgtot_6.4)
# 23224320  14

```

# Combine all values into a single data table

This part is broken into several smaller steps, but essentially we want to merge observation data and simplify the catch data. Calculate the total catch size and aggregate.

```{r catch.table, echo=TRUE}

# For Catch Weight by métier:
catch_year_group_metier <- setNames(aggregate(value~metier+YEAR+group+simu+InitialAbundance+Recruitment+Connectivity+Scenarios,data=catchWgtot_6.4,sum),c("METIER","YEAR","GROUP","simu","InitialAbundance","Recruitment","Connectivity","Scenarios","Catch_wg"))

catch_check1 <- subset(catch_year_group_metier, InitialAbundance == 0 & Recruitment == 0 & Connectivity == 0 & Scenarios == 16 & YEAR %in% c(2020, 2024))

catch_check1.1 <- aggregate(Catch_wg ~ YEAR + METIER, data = catch_check1, FUN = sum)

```

# Isolate the reference scenario (StatusQuo with original params)

Checking against the simulated results from the compiled data here and ISIS-Fish terminal, the same output is achieved. Here we choose StatusQuo scenario and the baseline assumptions for recruitment, initial abundance, or connectivity.

```{r key.binding, echo=TRUE}

catch_year_group_metier$CombiSimu <- 
  paste0("Init", catch_year_group_metier$InitialAbundance,
         "_Recr",catch_year_group_metier$Recruitment,
         "_Conn", catch_year_group_metier$Connectivity,
         "_Scen",catch_year_group_metier$Scenarios)

catch_Ref_metier <- catch_year_group_metier[catch_year_group_metier$CombiSimu == "Init0_Recr0_Conn0_Scen0",]

catch_Ref_metier <- as.data.frame(catch_Ref_metier[,c("METIER","YEAR","GROUP","Catch_wg")])

names(catch_Ref_metier)[4] <- "Catch_ref_wg"

catch_avec_ref_metier <- left_join(catch_year_group_metier, catch_Ref_metier,by=c("METIER","YEAR","GROUP"))

# select only of reference simulations (cad: Init=0, Rec=0, Conn=0)
catch_avec_ref_metier <- catch_avec_ref_metier[(catch_avec_ref_metier$InitialAbundance=="0" & catch_avec_ref_metier$Recruitment=="0" & catch_avec_ref_metier$Connectivity=="0"),]

catch_avec_ref_metier <- as.data.table(catch_avec_ref_metier) 

catch_year_ref_metier_part1 <- catch_avec_ref_metier[,list(Catch_sim_wg = sum(Catch_wg), Catch_ref_wg = sum(Catch_ref_wg)), by = list(METIER,YEAR, simu, InitialAbundance, Recruitment, Connectivity, Scenarios)]

```

# Create fleets 

Note that for simplicity, we are reclassifying and generalizing fleets to demonstrate catch differences.

```{r psuedo.fleet.summary, echo=TRUE}

unique(catch_year_ref_metier_part1$METIER)
colnames(catch_year_ref_metier_part1)

catch_avec_ref_fleet <- catch_year_ref_metier_part1 %>% 
  group_by(METIER) %>%
  mutate(Gear = strsplit(METIER, "_")[[1]][1], Port = strsplit(METIER, "_")[[1]][2]) %>%
  ungroup()

unique(catch_avec_ref_fleet$Port)

unique(catch_avec_ref_fleet$Scenarios)

```

For French Trawlers, isolate and compute CPUE.

```{r French.trawl.fleet, echo=TRUE}

Catch_fleet_French.trawl <- catch_avec_ref_fleet %>% 
  filter(!Gear %in% c("LLS","GNS") & Port != "ESP") %>%
  mutate(fleet = "French Trawlers") %>%
  group_by(Scenarios, fleet, YEAR) %>%
  summarise(Catch_sim_wg = sum(Catch_sim_wg), .groups = "keep") %>%
  ungroup()

Ref.Catch_fleet_French.trawl.agg <- Catch_fleet_French.trawl %>%
  filter(Scenarios == 0) %>%
  group_by(YEAR, fleet) %>%
  summarise(Catch_sim_wg = sum(Catch_sim_wg)) %>%
  ungroup() %>%
  mutate(YEAR = as.character(YEAR))

Ref.Catch_fleet_French.trawl <- Ref.Catch_fleet_French.trawl.agg %>%
  filter(YEAR <="2017") %>%
  mutate(Catch_ref_wg_mean = mean(Catch_sim_wg)) %>%
  dplyr::select(Catch_ref_wg_mean, fleet)

catch_year_ref.French.trawl <- full_join(Catch_fleet_French.trawl, Ref.Catch_fleet_French.trawl, by=c("fleet")) %>%
  mutate(Rel_Diff_wg = (Catch_sim_wg - Catch_ref_wg_mean) / Catch_ref_wg_mean * 100) %>%
  dplyr::select(c("YEAR","fleet","Scenarios","Rel_Diff_wg"))

unique(is.na(catch_year_ref.French.trawl))

catch_year_ref.French.trawl.part2 <- catch_year_ref.French.trawl %>%
  mutate(Scenarios = as.factor(Scenarios)) %>% 
  inner_join(.,table_Sce_6.4,by=c("Scenarios")) %>% 
  mutate(SceName = factor(SceName, levels = table_Sce_6.4$SceName))

```

For French Gillnetters, isolate and compute CPUE.

```{r French.gillnetter.fleet, echo=TRUE}

Catch_fleet_French.gillnetters <- catch_avec_ref_fleet %>% 
  filter(Gear == "GNS" & Port != "ESP") %>%
  mutate(fleet = "French Gillnetters")

Ref.Catch_fleet_French.gillnetters.agg <- Catch_fleet_French.gillnetters %>%
  filter(Scenarios == 0) %>%
  group_by(YEAR, fleet) %>%
  summarise(Catch_sim_wg = sum(Catch_sim_wg)) %>%
  ungroup() %>%
  mutate(YEAR = as.character(YEAR))

Ref.Catch_fleet_French.gillnetters <- Ref.Catch_fleet_French.gillnetters.agg %>%
  filter(YEAR <="2017") %>%
  mutate(Catch_ref_wg_mean = mean(Catch_sim_wg)) %>%
  dplyr::select(Catch_ref_wg_mean, fleet)

catch_year_ref.French.gillnetters <- full_join(Catch_fleet_French.gillnetters, Ref.Catch_fleet_French.gillnetters, by=c("fleet")) %>%
  mutate(Rel_Diff_wg = (Catch_sim_wg - Catch_ref_wg_mean) / Catch_ref_wg_mean * 100) %>%
  dplyr::select(c("YEAR","fleet","Scenarios","Rel_Diff_wg"))

unique(is.na(catch_year_ref.French.gillnetters))

catch_year_ref.French.gillnetters.part2 <- catch_year_ref.French.gillnetters %>%
  mutate(Scenarios = as.factor(Scenarios)) %>%
  inner_join(.,table_Sce_6.4,by=c("Scenarios")) %>% 
  mutate(SceName = factor(SceName, levels = table_Sce_6.4$SceName))

```

For Spanish Trawlers, isolate and compute CPUE.

```{r Spanish.trawl.fleet, echo=TRUE}

Catch_fleet_Spanish.trawl <- catch_avec_ref_fleet %>% 
  filter(Gear == "OTB" & Port == "ESP") %>%
  mutate(fleet = "Spanish Trawlers")

Ref.Catch_fleet_Spanish.trawl.agg <- Catch_fleet_Spanish.trawl %>%
  filter(Scenarios == 0) %>%
  group_by(YEAR, fleet) %>%
  summarise(Catch_sim_wg = sum(Catch_sim_wg)) %>%
  ungroup() %>%
  mutate(YEAR = as.character(YEAR))

Ref.Catch_fleet_Spanish.trawl <- Ref.Catch_fleet_Spanish.trawl.agg %>%
  filter(YEAR <="2017") %>%
  mutate(Catch_ref_wg_mean = mean(Catch_sim_wg)) %>%
  dplyr::select(Catch_ref_wg_mean, fleet)

catch_year_ref.Spanish.trawl <- full_join(Catch_fleet_Spanish.trawl, Ref.Catch_fleet_Spanish.trawl, by=c("fleet")) %>%
  mutate(Rel_Diff_wg = (Catch_sim_wg - Catch_ref_wg_mean) / Catch_ref_wg_mean * 100) %>%
  dplyr::select(c("YEAR","fleet","Scenarios","Rel_Diff_wg"))

unique(is.na(catch_year_ref.Spanish.trawl))

catch_year_ref.Spanish.trawl.part2 <- catch_year_ref.Spanish.trawl %>%
  mutate(Scenarios = as.factor(Scenarios)) %>%
  inner_join(.,table_Sce_6.4,by=c("Scenarios")) %>% 
  mutate(SceName = factor(SceName, levels = table_Sce_6.4$SceName))

```

For Spanish Longliners, isolate, and compute CPUE.

```{r spanish.longliner.fleet, echo=TRUE}

Catch_fleet_Spanish.longliners <- catch_avec_ref_fleet %>% 
  filter(Gear == "LLS" & Port == "ESP") %>%
  mutate(fleet = "Spanish longliners")

Ref.Catch_fleet_Spanish.longliners.agg <- Catch_fleet_Spanish.longliners %>%
  filter(Scenarios == 0) %>%
  group_by(YEAR, fleet) %>%
  summarise(Catch_sim_wg = sum(Catch_sim_wg)) %>%
  ungroup() %>%
  mutate(YEAR = as.character(YEAR))

Ref.Catch_fleet_Spanish.longliners <- Ref.Catch_fleet_Spanish.longliners.agg %>%
  filter(YEAR <="2017") %>%
  mutate(Catch_ref_wg_mean = mean(Catch_sim_wg)) %>%
  dplyr::select(Catch_ref_wg_mean, fleet)

catch_year_ref.Spanish.longliners <- full_join(Catch_fleet_Spanish.longliners, Ref.Catch_fleet_Spanish.longliners, by=c("fleet")) %>%
  mutate(Rel_Diff_wg = (Catch_sim_wg - Catch_ref_wg_mean) / Catch_ref_wg_mean * 100) %>%
  dplyr::select(c("YEAR","fleet","Scenarios","Rel_Diff_wg"))

unique(is.na(catch_year_ref.Spanish.longliners))

catch_year_ref.Spanish.longliners.part2 <- catch_year_ref.Spanish.longliners %>%
  mutate(Scenarios = as.factor(Scenarios)) %>%
  inner_join(.,table_Sce_6.4,by=c("Scenarios")) %>% 
  mutate(SceName = factor(SceName, levels = table_Sce_6.4$SceName))

```

# Prepare new data frame

Merge new fleet definition data.frames.

```{r bind.rows, echo=TRUE}

catch_year_ref_fleet_part2 <- rbind(catch_year_ref.French.trawl.part2, catch_year_ref.French.gillnetters.part2, catch_year_ref.Spanish.trawl.part2, catch_year_ref.Spanish.longliners.part2)

```

# Create groups by scenario type

The original study investigates 28 scenario measures and 504 combinations. But we simplify this here for the international audience.

```{r group.scen, echo=TRUE}

dim(catch_year_ref_fleet_part2)
Scenario_type <- seq(1:3360)

catch_year_ref_fleet_part2 <- cbind(catch_year_ref_fleet_part2, Scenario_type)

View(catch_year_ref_fleet_part2)

catch_year_ref_fleet_part2$Scenario_type <- 
  replace(catch_year_ref_fleet_part2$Scenario_type,c(1:30,841:870,1681:1710,2521:2550),"StatusQuo")

catch_year_ref_fleet_part2$Scenario_type <- 
  replace(catch_year_ref_fleet_part2$Scenario_type,c(31:120,871:960,1711:1800,2551:2640),"All-at-once Trawler Effort Reduction")

catch_year_ref_fleet_part2$Scenario_type <- 
  replace(catch_year_ref_fleet_part2$Scenario_type,c(211:300,1051:1140,1891:1980,2731:2820),"All-at-once Effort Reduction Applied to All Gears")

catch_year_ref_fleet_part2$Scenario_type <- 
  replace(catch_year_ref_fleet_part2$Scenario_type,c(121:210,961:1050,1801:1890,2641:2729),"Gradual Trawler Effort Reduction")

catch_year_ref_fleet_part2$Scenario_type <- 
  replace(catch_year_ref_fleet_part2$Scenario_type,c(301:390,1141:1230,1981:2070,2821:2910),"Gradual Effort Reduction Applied to All Gears")

catch_year_ref_fleet_part2$Scenario_type <- 
  replace(catch_year_ref_fleet_part2$Scenario_type,c(421:450,481:510,541:570,1261:1290,1321:1350,1381:1410,2101:2130,2161:2190,2221:2250,2941:2970,3001:3030,3061:3090),"Seasonal Spatial Closure Single Effects")

catch_year_ref_fleet_part2$Scenario_type <- 
  replace(catch_year_ref_fleet_part2$Scenario_type,c(391:420,451:480,511:540,571:600,1231:1260,1291:1320,1351:1380,1411:1440,2071:2100,2131:2160,2191:2220,2251:2280,2911:2940,2971:3000,3031:3060,3091:3120),"Annual Spatial Closure Single Effects")

catch_year_ref_fleet_part2$Scenario_type <- 
  replace(catch_year_ref_fleet_part2$Scenario_type,c(601:660,1441:1500,2281:2340,3121:3180),"With 90-100m Isobaths Spatial Closure Combined Effects")

catch_year_ref_fleet_part2$Scenario_type <- 
  replace(catch_year_ref_fleet_part2$Scenario_type,c(751:780,1591:1620,2431:2460,3271:3300,721:750,1561:1590,2401:2430,3241:3270),"Without 90-100m Isobaths Spatial Closure Combined Effects")

catch_year_ref_fleet_part2$Scenario_type <- 
  replace(catch_year_ref_fleet_part2$Scenario_type,c(661:720,1501:1560,2341:2400,3181:3240),"Spatial Closure and Effort Reduction Combined Effects With the 90-100m Isobaths Closure")

catch_year_ref_fleet_part2$Scenario_type <- 
  replace(catch_year_ref_fleet_part2$Scenario_type,c(781:840,1621:1680,2461:2520,3301:3360),"Spatial Closure and Effort Reduction Combined Effects Without the 90-100m Isobaths Closure")

catch_year_ref_fleet_part2.df <- as.data.frame(catch_year_ref_fleet_part2)

catch_year_ref_fleet_part2.df$Scenario_type <- as.factor(catch_year_ref_fleet_part2.df$Scenario_type)

# View(catch_year_ref_fleet_part2.df)

```

Reorder the groups that we are interested in.

```{r reorder, echo=TRUE}

catch_year_ref_fleet_part2.df_reorder <- 
  catch_year_ref_fleet_part2.df %>% mutate(
    SceName_short = 
      recode_factor(SceName,
                  "StatusQuo"= "a",
                  "Trawler_30_Red"= "b",
                  "AllGears_30_Red" = "c",
                  "Trawler_40_Red" = "d",
                  "AllGears_40_Red"= "e",
                  "Trawler_50_Red"= "f",
                  "AllGears_50_Red"= "g",
                  "Trawler_10_20_30"= "h",
                  "AllGears_10_20_30"= "i",
                  "Trawler_10_17.5_25_32.5_40"= "j",
                  "AllGears_10_17.5_25_32.5_40"= "k",
                  "Trawler_10_20_30_40_50"= "l",
                  "AllGears_10_20_30_40_50"= "m",
                  "Original_FRA_allYear"= "n",
                  "Northward_Expansion_of_FRA_Season"= "o",
                  "Northward_Expansion_of_FRA_allYear" = "p",
                  "90-100_Isobaths_Closure_Season"= "q",
                  "90-100_Isobaths_Closure_allYear"= "r", 
                  "Offshore_Closures_Season"= "s",
                  "Offshore_Closures_allYear"= "t",
                  "Northward_Expansion_of_FRA_90-100m_Offshore_Closures_Combined"= "u",
                  "Northward_Expansion_of_FRA_Offshore_Closures_Combined" = "v",
                  "Northward_Expansion_of_FRA_90-100m_Offshore_allYear_Closures_Combined" = "w",
                  "Northward_Expansion_of_FRA_Offshore_allYear_Closures_Combined" = "x",
                  "Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_90-100m_Offshore_Closures"= "y",
                  "Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_Offshore_Closures"= "z",
                  "Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_90-100m_Offshore_Closures_allGears"= "aa",
                  "Combined_Red_10_17.5-40_Northward_Expansion_of_FRA_Offshore_Closures_allGears"= "bb"
                ))

```

Save special group output.

```{r save.output, echo=TRUE}

fwrite(catch_year_ref_fleet_part2.df_reorder, file=paste(path, "fleet.catch.weight.by.year.csv", sep=""), sep=";")

```
